Blame and Coercion: Together Again for the Second Time

### 2019-10-14 paper.tex
fix typos in figs
part of the machine section

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\newcommand{\GTLC}{\texttt{GTLC+}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
\newcommand{\redrule}[3]{#1 & \longrightarrow_B & #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
\newcommand{\lazyD}{$\mathtt{Lazy D}$}
\newcommand{\eager}{$\mathtt{Eager}$}
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{#1 \; #2}
\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}

@@

Implementing gradually typed languages naively on top of blame calculus 
suffices sever space leak.
For example, translation to Blame Calculus can wrap some expressions with a 
cast, including those at tail position. Thus, at runtime, mutually 
tail-recursive functions in source language can accumulate casts at tail 
position. There are more examples in \citet{herman2010space}.

@@

\citet{siek2009exploring} incorporate blame tracking into Coercion Calculus by 
decorating coercions with labels. They also propose that there are four blame 
strategies for their Coercion Calculi:
$ \{Lazy, Eager\} \times \{D, UD\} $. 
Eager strategies detect more potential type errors, 
but also blame more programs.
$ D $ and $ UD $ assign blame labels differently.
They prove partially that the \lazyUD{} Coercion Calculus is correct by showing 
that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
however, whether the simulation also works the other direction.

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution is based on Threesome Calculus. 
Their key idea is to represent casts with threesomes, a novel cast 
representation.
%Threesomes can also be composed. Unlike coercions, there is no 
%separate normalization because every threesome is in normal form. 
They prove that their Threesome Calculus is correct by showing it bi-simulates
the \lazyUD{} Coercion Calculus in \citet{siek2009exploring} and the Blame 
Calculus in \citet{wadler2009well}.
They also prove that threesome is space-efficient as well.

@@

Following \citet{siek2010threesomes}, \citet{garcia2013calculating} discovers
Threesome Calculi for other blame strategies. After studying the relation 
between coercion and threesome,
he claims that normal coercion with labels is easy to understand but hard to 
implement and hard to reason about, and that 
threesome with labels, however, is easy to implement and easy to reason about 
but hard to understand. 
His claim is later affirmed by the group of people who develop threesome 
(\citet{siek2015blame}).
His threesome calculi are equivalent to the Coercion Calculi in 
\citet{siek2009exploring} because the former ones are derived from the latter 
ones.

\citet{siek2015blame} revisit the coercion-based approach. They revise the 
\lazyUD{} Coercion Calculus in \citet{siek2012interpretations}.
They prove that their calculus agrees with the \lazyUD{} Blame Calculus.

@@

So far, it seems that the coercion-based approach is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least three aspects.
Firstly, as we mentioned above, it is hard to reason about. The major 
difficulty is from its non-structurally recursive composition.
For instance, many developers of Grift report convincing
their proof assistants that the composition terminates is tricky. 
Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown that there exist functions that 
compose and produce normal coercions.

@@

By comparing hyper-coercion with normal coercion, we notice another problem of 
the latter in memory representation. \dots

@@

\subsection{$Lazy UD$ Blame Calculus [Jeremy]}

@@

\subsection{$Lazy D$ Coercion Calculus}

\subsection{$Lazy UD$ Coercion Calculus}

@@

@@

	\comprule{
		\hyperCoercionI
	}{
		\hyperCoercionC{?^{l'}}{b}{t}
	}{
		\hyperCoercionC{?^{l'}}{b}{t}
	}{}

	\comprule{
		\hyperCoercionI
	}{
		\hyperCoercionC{\epsilon}{b}{t}
	}{
		\hyperCoercionC{?^{l}}{b}{t}
	}{\sidecond{\ell = l}}

	\comprule{
		\hyperCoercionC{h}{b}{\bot^{l'}}
	}{
		c
	}{
		\hyperCoercionC{h}{b}{\bot^{l'}}
	}{}

	\comprule{
		\hyperCoercionC{h}{b_1}{t_1}
	}{
		\hyperCoercionI
	}{
		\hyperCoercionC{h}{b_1}{!}
	}{
		\sidecond{\forall l. t_1 \neq \bot^{l}}
	}

	\comprule{
		\hyperCoercionC{h}{b_1}{t_1}
	}{
		\hyperCoercionC{\epsilon}{b_2}{t_2}
	}{
		\hyperCoercionC{h}{b'}{t'}
	}{
		\sidecond{
			t_1 \neq \bot^{\centerdot} \; \text{and} \;
			b_1 \fatsemi^{\ell} (b_2, t) = (b', t')
		}
	}

	\comprule{
		\hyperCoercionC{h}{b_1}{t_1}
	}{
		\hyperCoercionC{?^{l'}}{b_2}{t_2}
	}{
		\hyperCoercionC{h}{b'}{t'}
	}{
		\sidecond{
		t_1 \neq \bot^{\centerdot} \; \text{and} \;
		b_1 \fatsemi^{l'} (b_2, t) = (b', t')
		}
	}
	\end{array}
	\]

@@

	\fbox{$ cast(T,l,T) = c$}
	\[
	\begin{array}{rclr}
	\funrule{cast(T_1,l,T_2)}{
		id(T_1) \fatsemi^l id(T_2)
	}{}
	\end{array}
	\]
	\caption{$Lazy D$ Hyper-coercion}
	\label{fig:HC-D}
\end{figure}

@@

To show that hyper-coercion is a correct cast representation, we introduce an 
hyper-coercion-based machine for the \lazyD\ blame calculus, and show that it 
bi-simulates the previous machine. 
\figref{machine-cekcc} defines the new machine.

	Reduction \fbox{$ s \longrightarrow_{D,P(C)} s $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redrule{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,P(C)}^{*} s $}
	\[\dots\]

	Evaluation \fbox{$ e \Downarrow_{D,P(C)} o $}
	\[
	\inference{
		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{P(C)}^{*} 
		\sOOhalt{o}
	}{
		e \Downarrow_{D,P(C)} o
	}
	\]

	\caption{An abstract machine that composes casts.}
	\label{machine-cekcc}
\end{figure}

Let $ v $ ranges over value. We push casts into values. For instance, function 
values now include two more components: a cast for argument and a cast for the 
output. The last kind of values is injection to $ \TOOdyn $. 
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
pre-continuations. 
A continuation is now a pair whose first part is a cast, and whose second part 
is a pre-continuation. 
Pre-continuation are like the continuations before.

@@

\subsection{$Lazy UD$ Hyper-coercion [Jeremy]}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max 
%%submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max 
%%submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\newcommand{\GTLC}{\texttt{GTLC+}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 &=& #2 & #3\\}
\newcommand{\redrule}[3]{#1 & \longrightarrow_B & #2 & #3\\}
\newcommand{\redruleS}[3]{#1 & \longrightarrow_{S(C)} & #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^\ell & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}
\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
\newcommand{\lazyD}{$\mathtt{Lazy D}$}
\newcommand{\eager}{$\mathtt{Eager}$}
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #1 \; #2 \; #3}
\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}
\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{#1 \; #2}
\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}
\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}

@@

Implementing gradually typed languages naively on top of blame calculus 
suffices sever space leak.
For example, translation to Blame Calculus can wrap some expressions with a 
cast, including those at tail position. Thus, at runtime, mutually 
tail-recursive functions in source language can accumulate unbounded space. 
There are more examples in \citet{herman2010space}.

@@

%\subsection{coercion-based approach and blame strategies}

\citet{siek2009exploring} incorporate blame tracking into 
\citet{herman2010space}'s Coercion Calculus by 
decorating coercions with labels. They also propose that there are four blame 
strategies for their Coercion Calculi:
$ \{Lazy, Eager\} \times \{D, UD\} $. 
Eager strategies detect more potential type errors, 
but also blame more programs.
$ D $ and $ UD $ assign blame labels differently.
They prove partially that the \lazyUD{} Coercion Calculus is correct by showing 
that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
however, whether the simulation also works in the other direction.

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution is based on Threesome Calculus. 
Their key idea is to represent casts with threesomes, a novel cast 
representation.
%Threesomes can also be composed. Unlike coercions, there is no 
%separate normalization because every threesome is in normal form. 
They show that their threesome calculus bi-simulates the \lazyUD{} Coercion 
Calculus in \citet{siek2009exploring} and the Blame Calculus in 
\citet{wadler2009well}. They also prove that threesome is space-efficient as 
well.

@@

Following \citet{siek2010threesomes}, \citet{garcia2013calculating} discovers
Threesome Calculi for other blame strategies. After studying the relation 
between coercion and threesome,
he claims that normal coercion with labels is easy to understand but hard to 
implement and hard to reason about, and that 
threesome with labels, however, is easy to implement and easy to reason about 
but hard to understand. 
His claim is partially affirmed by the group of people who develop threesome 
(\citet{siek2015blame}).
His threesome calculi are equivalent to the Coercion Calculi in 
\citet{siek2009exploring} because the former ones are derived from the latter 
ones.

\citet{siek2015blame} revisit the coercion-based approach. They revise the 
\lazyUD{} Coercion Calculus in \citet{siek2012interpretations} and prove that 
their revised coercion calculus bi-simulates the \lazyUD{} Blame Calculus.

@@

So far, it seems that the coercion-based approach is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least three aspects.
Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
major difficulty is from its non-structurally recursive composition.
For instance, many developers of Grift report it is tricky to convince
their proof assistants that the composition terminates. 
Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown that there exist functions that 
compose and produce normal coercions.

@@

@@

\subsection{\lazyUD{} Blame Calculus [Jeremy]}

@@

\subsection{\lazyD{} Coercion Calculus}

\subsection{\lazyUD{} Coercion Calculus}

@@

All definitions and results in this section are new.

We present a space-efficient CEK machine for blame calculi. This machine is
parameterized over cast representation.

	Reduction \fbox{$ s \longrightarrow_{S(C)} s $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

%	Transitive closure of reduction \fbox{$ s \longrightarrow_{S(C)}^{*} s $}
%	\[\dots\]

	Evaluation \fbox{$ e \Downarrow_{S(C)} o $}
	\[
	\inference{
		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{S(C)}^{*} 
		\sOOhalt{o}
	}{
		e \Downarrow_{S(C)} o
	}
	\]

	\caption{A space-efficient CKE machine for Blame Calculus.}
	\label{machine-cekcc}
\end{figure}

\figref{machine-cekcc} defines the machine. 
Let $ v $ ranges over value. We push casts into values. For instance, function 
values now include two more components: a cast for argument and a cast for the 
output. The last kind of values is injection to $ \TOOdyn $. 
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
pre-continuations. 
A continuation is now a pair whose first part is a cast, and whose second part 
is a pre-continuation. 
Pre-continuation are like the continuations before.

\subsection{\lazyD\ Cast Representations}

We show that all \textit{proper} cast representations are 
equivalent.

With the properties of proper cast representation, it is straightforward to 
proof that all machines instantiated with a proper cast representation are 
strongly bi-simulated.

\begin{theorem}[Strong Bi-simulation of Proper Cast Representations]
	If $ C_1 $ and $ C_2 $ are proper cast representations,
	$ s_1 $ and $ s_2 $ are states of $ S(C_1) $,
	$ s_3 $ is an state of $ S(C_2) $,
	$ s_1 \longrightarrow_{S(C_1)} s_2 $,
	and $ s_1 \approx s_3 $, \\
	then there exists an $ s_4 $ such that $ s_3 \approx s_4 $ and
	$ s_3 \longrightarrow_{S(C_2)} s_4 $
\end{theorem}

As a corollary, machines instantiated with proper cast representations are 
equivalent when used as interpreters.

\begin{theorem}[proper cast represenations are equivalent]
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and that $ C_1 $ and $ C_2 $ 
	are 
	proper cast representations
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{theorem}

@@

	\comprule{
		\hyperCoercionI
	}{
		\hyperCoercionC{?^{l'}}{m}{t}
	}{
		\hyperCoercionC{?^{l'}}{m}{t}
	}{}

	\comprule{
		\hyperCoercionI
	}{
		\hyperCoercionC{\epsilon}{m}{t}
	}{
		\hyperCoercionC{?^{l}}{m}{t}
	}{\sidecond{\ell = l}}

	\comprule{
		\hyperCoercionC{h}{m}{\bot^{l'}}
	}{
		c
	}{
		\hyperCoercionC{h}{m}{\bot^{l'}}
	}{}

	\comprule{
		\hyperCoercionC{h}{m}{t}
	}{
		\hyperCoercionI
	}{
		\hyperCoercionC{h}{m}{!}
	}{
		\sidecond{\forall l. t \neq \bot^{l}}
	}

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{\epsilon}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
			t_1 \neq \bot^{\centerdot} \; \text{and} \;
			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
		}
	}

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{?^{l'}}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
		t_1 \neq \bot^{\centerdot} \; \text{and} \;
		m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
		}
	}
	\end{array}
	\]

@@

	\fbox{$ cast(T,l,T) = c$}
	\[
	\begin{array}{rclr}
	\funrule{cast(T_1,l,T_2)}{
		id(T_1) \fatsemi^l id(T_2)
	}{}
	\end{array}
	\]
	\caption{\lazyD{} Hyper-coercion}
	\label{fig:HC-D}
\end{figure}

@@

To show that hyper-coercion is a correct cast representation, we introduce an 
hyper-coercion-based machine for the \lazyD\ blame calculus, and show that it 
bi-simulates the previous machine.

@@

\subsection{\lazyUD{} Hyper-coercion [Jeremy]}
